Gamification Effectiveness on Education

### 2024-04-17 paper/paper.qmd
renamed figures to match our paper and finish the rough draft for the data section

This paper reproduces the result from @DEMARCOS2017155. This paper will provided a overview of the data used in that study. For more detailed explanation of the data please visit the original study(insert link).

@@

The control group just use what was mention above. Educational game used was called Ribbonhero offered by Microsoft as as free download to download Software, and player plays as virtual character Clippy and must overcome six challenges with increasing difficulty. Gamification plugin (@fig-Gamification-plugin) is integrated in the institutional management system where there are challenges, trophies/badges and a leader board. Social Networking website was run on a open source engine, Elgg (@fig-social_network) and it functions very similar to social media where students can share their thoughts, make friends and discuss the material in class. Social gamified networking website use the same engine as the previous group and having similar features to Gamification plugin(@fig-social_gamification). A summary of the groups features and potential benefits(@tb-summary-group). The study highlights that the educational game is not necessarily aligned with the learning goals, while the gamification used in this study was.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-Gamification-plugin
#| fig-cap: "Gamifcation Plugin. Leaderboard and challenges."
knitr::include_graphics(file.path(here::here(),"other/figures/figure1.jpg")) 
```
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-social_network
#| fig-cap: "Social Networking Website."
knitr::include_graphics(file.path(here::here(),"other/figures/figure2.jpg")) 
```
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-social_gamification
#| fig-cap: "Social gamification website: Gamification tools (left), dashboard (top-right) & leaderboard (bottom-right)."
knitr::include_graphics(file.path(here::here(),"other/figures/figure3.jpg")) 
```
```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: tb-summary-group
#| tbl-cap: "Summary of the groups used, their features and potential benefits."

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: tb-pretest
#| tbl-cap: "The results of the pretest."

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: tb-posttest
#| tbl-cap: "The results of the posttest."

htmltools::includeHTML(file.path(here::here(),"other/tables/table3.html"))
```
The variables that are we are interested in seeing if share a relationship is posttest of Word Processing, Spreadsheets, Presentations, Databases and final examination. And we are interested in seeing the difference between the pretest(@tb-pretest) and posttest(@tb-posttest) and how each group is affect by the experiment.

The results from pretest(@tb-pretest) are pretty such the same for each group which aligns with the fact that this study was given before the experiment began. When looking at the post test results(@fig-boxplot), the control group is lagging behind the other groups, especially in word processing, spreadsheets and databases.

@@

In database post test(@fig-boxplot), the educational game performed as worse the control group. And similarly to the presentation posttest the social gamification does worse than the social network and gamification plugin. And gamification plugin does slightly better than social network.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-boxplot
#| fig-cap: "Boxplot showing the results of the post test for control and experiment groups "
knitr::include_graphics(file.path(here::here(),"other/figures/figure5.png"))

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))

>>>>

This paper reproduces the result from called "On the effectiveness of game-like and social approaches in learning: Comparing educational gaming, gamification & social networking" (@DEMARCOS2017155). This paper will provided a overview of the data used in that study. For more detailed explanation of the data please visit the original study.

@@

The control group just use what was mention above. Educational game used was called Ribbonhero offered by Microsoft as as free download to download Software, and player plays as virtual character Clippy and must overcome six challenges with increasing difficulty. Gamification plugin (@fig-Gamification-plugin) is integrated in the institutional management system where there are challenges, trophies/badges and a leader board. Social Networking website was run on a open source engine, Elgg (@fig-social_network) and it functions very similar to social media where students can share their thoughts, make friends and discuss the material in class. Social gamified networking website use the same engine as the previous group and having similar features to Gamification plugin(@fig-social_gamification). A summary of the groups features and potential benefits(@tbl-summary-group). The study highlights that the educational game is not necessarily aligned with the learning goals, while the gamification used in this study was.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-Gamification-plugin
#| fig-cap: "Gamifcation Plugin. Leaderboard and challenges."
knitr::include_graphics(file.path(here::here(),"other/figures/figure1.jpg")) 
```
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-social_network
#| fig-cap: "Social Networking Website."
knitr::include_graphics(file.path(here::here(),"other/figures/figure2.jpg")) 
```
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-social_gamification
#| fig-cap: "Social gamification website: Gamification tools (left), dashboard (top-right) & leaderboard (bottom-right)."
knitr::include_graphics(file.path(here::here(),"other/figures/figure3.jpg")) 
```
```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: tbl-summary-group
#| tbl-cap: "Summary of the groups used, their features and potential benefits."

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: tbl-pretest
#| tbl-cap: "The results of the pretest."

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: tbl-posttest
#| tbl-cap: "The results of the posttest."

htmltools::includeHTML(file.path(here::here(),"other/tables/table3.html"))
```
The variables that are we are interested in seeing if share a relationship is posttest of Word Processing, Spreadsheets, Presentations, Databases and final examination. And we are interested in seeing the difference between the pretest(@tbl-pretest) and posttest(@tbl-posttest) and how each group is affect by the experiment.

The results from pretest(@tbl-pretest) are pretty such the same for each group which aligns with the fact that this study was given before the experiment began. When looking at the post test results(@fig-boxplot), the control group is lagging behind the other groups, especially in word processing, spreadsheets and databases.

@@

In database post test(@fig-boxplot), the educational game performed as worse the control group. And similarly to the presentation posttest the social gamification group does worse than the social network and gamification plugin. And gamification plugin does slightly better than social network.

For the final examination(@fig-final-examination), interestingly enough, the group with the best results was the control group. Followed closely, by the social network group and then Educational game group. So the groups that performed the worse was gamfication plugin group and social gamfication group.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-boxplot
#| fig-cap: "Boxplot showing the results of the post test for control and experiment groups "
knitr::include_graphics(file.path(here::here(),"other/figures/figure4.png"))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-final-examination
#| fig-cap: "Boxplot showing the results of the final examination for each group that particapte in this experiment"
knitr::include_graphics(file.path(here::here(),"other/figures/figure5.png"))
